MyStoryKnight: A Character-drawing Driven Storytelling System Using LLM Hallucinations

### 2023-12-22 paper_interaction_conf/main.tex
Refactor storytelling system to generate interactive stories using character drawings

\begin{abstract}
    Storytelling is a valuable tradition that plays a crucial role in child development, fostering creativity and a sense of agency. However, many parents struggle to engage in interactive storytelling due to various constraints. As a result, children often consume stories passively, missing out on the opportunity to participate in the creative process. To address this, we propose MyStoryKnight, a character drawing driven storytelling system. By leveraging LLM hallucinations, our system generates adventure-type stories that allow users to navigate and make choices. Through a complexity analysis algorithm, we ensure the coherence and consistency of the generated stories, resulting in engaging and easily comprehensible narratives.
\end{abstract}

>>>>

\begin{abstract}
    Storytelling is a valuable tradition that plays a crucial role in child development, fostering creativity and a sense of agency. However, many children often consume stories passively, missing out on the opportunity to participate in the creative process. To address this, we propose a storytelling system that creates adventure-type stories with multiple branches that users can explore. We generate these interactive stories using a character drawing as input, with visual features extraction using GPT-4. By leveraging LLM hallucinations, we generate interactive stories using user feedback as a prompt. Finally, we refine the quality of the generated story through a complexity analysis algorithm. We believe that the use of a drawing as input further improves the engagement in the story and characters.
\end{abstract}
